\vspace{-2mm}
\section{Discussion}
\vspace{-3mm}
We introduce the first provably convergent
algorithm for the TRW objective over the marginal polytope, 
under the assumption of exact MAP oracles.
%
%
We quantify the gains obtained both from marginal inference over $\MARG$ \textit{and} from tightening
over the spanning tree polytope. 
%
%
We give heuristics that improve the scalability of Frank-Wolfe
when used for marginal inference.
The runtime cost of iterative MAP calls (a reasonable rule of thumb is to assume 
an approximate MAP call takes roughly the same time as a run of TRBP) is worthwhile particularly in 
%
%
cases such as the Chinese Characters where $\LOCAL$ is loose. 
Specifically, our algorithm is appropriate for domains where marginal inference is hard but there exist
efficient MAP solvers capable of handling non-submodular potentials.
Code is available at {\small \url{https://github.com/clinicalml/fw-inference}}. 

Our work creates a flexible, modular framework for optimizing a broad
class of variational objectives, not simply TRW, with guarantees of convergence. We hope that this
will encourage more research on building better entropy approximations.
%
%
%
The framework we adopt is more generally applicable
to optimizing functions whose gradients tend to infinity at the boundary of the
domain.
%
%

%
%
%
%

Our method to deal with gradients that diverge at the boundary
bears resemblance to barrier functions used in interior point methods insofar as they bound
the solution away from the constraints. Iteratively decreasing $\shrinkAmount$ in our framework
can be compared to decreasing the strength of the barrier, enabling the iterates to get closer to the
facets of the polytope, although its worthwhile to note that we have an \emph{adaptive} method of doing so.
