\section{SVM training for clip retrieval}
\label{app:svm}

In Section~\ref{sec:exp_weak} we proposed an automatic method for retrieving video clips with manipulated objects.
This method makes use of narrations that come along with instructional videos. 
Narrations in the form of text are first obtained \emph{automatically} with Automatic Speech Recognition (ASR)\footnote{The ASR transcriptions are directly downloaded from YouTube.} and then processed as detailed below.

\textbf{Language dataset.}
For each manipulation action, we first find relevant positive and negative sentences on instruction websites such as Wikihow.
On average we obtain about 12 positive and 50 negative sentences per action.

\textbf{Language features.}
Off-the-shelf methods for text parsing typically fail in the absence of punctuation.
To process ASR output, which comes without punctuation, we propose to use the following simple but robust text representation. 
We represent every 10-word window of the narration by a TF-IDF vector based of uni-grams and bi-grams.
We use the same TF-IDF representation to encode text in our Language dataset on the level of sentences.

\textbf{SVM training.}
We train binary linear SVM classifiers to identify manipulation actions using the Language dataset for training and the regularization parameter $C=10$.
The obtained classifiers are then used to score every 10-word window of text narrations.
Video clips with the temporal correspondence to the top-scoring text narrations for each action are then retrieved. 
To deduce the temporal extent of the video clip given the top-scoring window, we trim 5 seconds before and 15 seconds after the corresponding timing.
This is to account for the fact that people are usually doing the action after speaking about it.
These are the clips we use for our evaluation in Section~\ref{sec:exp_weak} of the main paper.

\textbf{Illustration.} 
In Figure~\ref{tab:svm_1}, we provide an illustration of text based clip retrieval.
This visualization demonstrates the difficulty of the addressed problem (see caption for details).




