\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage{subfloat}
\usepackage{titling}
\usepackage{iccv}
\usepackage{soul}
\usepackage{array}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
%
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs,siunitx}
\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{subcaption}
\usepackage{footmisc}

\soulregister\cite7
\soulregister\ref7



%
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\DeclareRobustCommand{\JB}[1]{{\sethlcolor{cyan}\hl{JB: #1}}}
%
\hypersetup{
  plainpages=false,
  %
  colorlinks=true,   			%
  linkcolor=blue,    			%
  anchorcolor=blue,  			%
  citecolor=blue,    			%
  filecolor=blue,    			%
  pagecolor=blue,    			%
  urlcolor=blue,     			%
  pdfview=FitH,                 %
  pdfstartview=FitH,            %
  pdfpagelayout=SinglePage      %
}

%
%
%
%
%
\DeclareMathOperator*{\argmin}{arg\,min}
\iccvfinalcopy

\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

%
\ificcvfinal\pagestyle{empty}\fi


%
\begin{document}

\title{Joint Discovery of Object States and Manipulation Actions}
\author{
Jean-Baptiste Alayrac\thanks{D\'{e}partement d’informatique de l'ENS, \'{E}cole normale sup\'{e}rieure, CNRS, PSL Research University, 75005
	Paris, France.} \ \thanks{INRIA}
\and
Josef Sivic\footnotemark[1] \ \footnotemark[2] \ \thanks{Czech Institute of Informatics, Robotics and Cybernetics at the
Czech Technical University in Prague.}
\and
Ivan Laptev\footnotemark[1] \ \footnotemark[2]
\and
Simon Lacoste-Julien\thanks{Department of CS \& OR (DIRO), Universit\'{e} de Montr\'{e}al, Montr\'{e}al.}
}
\maketitle
\begin{abstract}
Many human activities involve object manipulations aiming to modify the object state.
Examples of common state changes include full/empty bottle, open/closed door, and attached/detached car wheel.
In this work, we seek to automatically discover the states of objects and the associated manipulation actions.
Given a set of videos for a particular task, we propose a joint model that learns to identify object states and to localize state-modifying actions.
Our model is formulated as a discriminative clustering cost with constraints.
We assume a consistent temporal order for the changes in object states and manipulation actions, 
and introduce new optimization techniques to learn model parameters without additional supervision.
We demonstrate successful discovery of seven manipulation actions and corresponding object states on a new dataset of videos depicting real-life object manipulations.
We show that our joint formulation results in an improvement of object state discovery by action recognition and vice versa.
%
%
%
%
%
%
%
%
%
\end{abstract}
\input{arxiv_intro.tex}
\input{arxiv_model.tex}
\input{optimization.tex}
\input{arxiv_experiment.tex}
\input{arxiv_conclusion.tex}

\footnotesize{
	\paragraph{Acknowledgments}
	This research was supported in part by a Google Research Award, ERC grants Activia (no. 307574) and LEAP (no. 336845), the CIFAR Learning in Machines \& Brains program and ESIF, OP Research, development and education Project IMPACT No. CZ.02.1.01/0.0/0.0/15 003/0000468.
}


{\small
\bibliographystyle{ieee}
\bibliography{biblio}
}


%
\clearpage
\appendix
\normalsize
\section*{Outline of Appendix}
%
This Appendix gives additional details and quantitative results for our method.
The organization is as follows.
In Appendix~\ref{app:svm}, we provide additional experimental details about the SVM training used to retrieve the clips with subtitles, described in Section~\ref{sec:exp_weak} of the main paper, along with a visualization of results.
In Appendix~\ref{app:dataset}, we give additional statistics and details about the dataset that was briefly introduced in Section~\ref{sec:dataset} of the main paper.
In Appendix~\ref{app:dp}, we give additional details about the dynamic program that we use to solve the linear program over the track constraints defined in Section~\ref{sec:statemodel} of the main paper as needed for the Frank-Wolfe optimization algorithm.
In Appendix~\ref{app:jcr}, we detail how we implement the \emph{new} joint rounding method~\eqref{eq:jcrrounding} that was introduced in Section~\ref{sec:joint} of the main paper.
In Appendix~\ref{app:supervised}, we give additional details about the supervised baselines results given in Section~\ref{sec:exp_res}.
Finally, in Appendix~\ref{app:failcases}, we comment on the common failure cases of the method.




%

\input{suppmat_svm.tex}
\input{suppmat_fig1.tex}
\input{suppmat_dataset.tex}
%
\input{suppmat_DP.tex}

%
\input{suppmat_roundingjcr.tex}

\input{suppmat_supervised.tex}

\input{suppmat_failurecases.tex}




\end{document}
